Eagle: Making multiple-locus association mapping on a genome-wide scale routine

### 2018-06-20 AM+draft.tex
20June18 rev3

 To calculate the power of a method, we averaged across the 100 replicates of a scenario where for each replicate, we divided the number of snp findings that were true by the number of selected (true) 
snp used in generating the trait data.  Similarly, to calculate a method's fdr, we averaged across the 100 replicates of a scenario where 
for each replicate, we divide the number of true snp found by the number of (true and false) snp found.

In Figure X, the power and fdrs of Eagle are compared to the other multiple locus methods. For a comparison with single-locus methods, 
see Sup Figure X. Each plot contains a mix of single points and power curves. The single points are the power and fdrs for Eagle and MLMM. 
These two methods treat association mapping as a model selection problem. Their are no significance thresholds to be set. 
In contrast, the other methods treat association mapping as a parameter estimation problem. As such, a threshold value is required before a snp 
can be deemed as being in significant association with a trait.  The challenge is in setting this significance threshold. The curves in Figure 
X and Sup Figure X  show how power changes with the fdr as the significance level (and resulting significance threshold) is allowed to vary.

 in order to determine which are significant findings.

before the truth of a snp result can be assessed.

This is not true for the other methods. They all require a significance threshold upon which to determine the truth of a finding. The power curves are formed from varying the threshold so that the significance level ranges from 99.9% to 0.1%.

>>>>

The power and fdr of Eagle and the other multiple-locus methods across the scenarios 150 x 5K, 350 x 500K, 1500 x 50K, and 2000 x 500K are shown in Figure X.  We restricted our attention to these scenarios for the multiple-locus methods because for scenario 4000 x 1.5M, 
the data could only be analysed by Eagle, MLMM, and r2VIM. For scenario 10000 x 1.5M, the data could only be analysed by Eagle. 
The power and fdr of Eagle and the two single-locus methods, GEMMA and FaST-LMM,  are shown in Sup Figure X.  Each plot contains 
single points and power curves. The single points are the power and fdrs for Eagle and MLMM.
These two methods treat association mapping as a model selection problem. Their are no significance thresholds to be set. 
The power curves are for those methods that treat association mapping as a parameter estimation problem. Here, the 
significance of the findings are assessed against a significance threshold. The power curves in the plot show how power changes with 
the fdr as the significance threshold (and underlying significance level) is varied.

In Figure X, the power and fdr of Eagle are compared to the other multiple locus methods. For a comparison with single-locus methods, 
see Sup Figure X. Each plot contains a mix of single points and power curves. The single points are the power and fdrs for Eagle and MLMM. 
These two methods treat association mapping as a model selection problem. Their are no significance thresholds to be set. 
In contrast, the other methods treat association mapping as a parameter estimation problem. As such, a threshold value is required before a snp 
can be deemed as being in significant association with a trait.  The challenge is in setting this significance threshold. The curves in Figure 
X and Sup Figure X  show how power changes with the fdr as the significance level (and resulting significance threshold) is allowed to vary.
